Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-07-15 manuscript.tex
Random data in discussion

Identification of cells sharing similar properties in single cell experiments is of paramount importance. A large number of approaches have been described, although the standardisation of analysis pipelines converged to methods that are based on modularity optimisation. We tackled the biological problem using a different approach, nSBM, which has several advantages over existing techniques. The most important advantage is the hierarchical definition of cell groups which eliminates the choice of an arbitrary threshold on clustering resolution. In addition, we showed that the hierarchy itself could have a biological interpretation, implying that the hierarchical model is a valid representation of the cell ensemble.

>>>>

Identification of cells sharing similar properties in single cell experiments is of paramount importance. A large number of approaches have been described, although the standardisation of analysis pipelines converged to methods that are based on modularity optimisation. We tackled the biological problem using a different approach, nSBM, which has several advantages over existing techniques. \textcolor{red}{As  random data may have modular structure \cite{guimer_2004}, an important property of our approach is that it does not overfit data by finding partitions when, in fact, the are not.} Another important advantage is \textcolor{that} the hierarchical definition of cell groups eliminates the choice of an arbitrary threshold on clustering resolution. In addition, we showed that the hierarchy itself could have a biological interpretation, implying that the hierarchical model is a valid representation of the cell ensemble.
